No Massive Companion to the low-frequency, coherent radio-emitting M~Dwarf GJ\,1151

### 2019-06-21 paper/ms.tex
callingham changes included

Exoplanet science has flourished over the last three decades. The number of known planets has doubled nearly every two years since 1995 \citep{Mamajek2016} and this accelerating rate of discovery is projected to continue for at least the next decade if current and upcoming space-based surveys deliver their expected results. However, despite extensive searches \citep[e.g.][]{2000ApJ...545.1058B,2013A&A...552A..65L,Lynch18}, neither exoplanets nor their host stars have been detected at radio frequencies, as the quiescent emission of such systems has been too faint for current telescopes \textcolor{red}{JRC - Not clear what you mean by quiescent here? E.g. Is ECMI quiescent emission?}. But as the Square Kilometre Array \citep[SKA;][]{2009IEEEP..97.1482D} and its precursors, in particular LOFAR \citep[the LOw-Frequency ARray:][]{lofar} come online \textcolor{red}{JRC - LOFAR has been operating for a decade, is not ``coming online''. I would drop the mention of SKA and just say LOFAR, an SKA-precursor, is unparalleled sensitivity at 150 MHz  where detections of such interaction are now possible and cite Zarka et al. (his scaling work)}, the orders-of-magnitude increase in sensitivity and survey speed they provide makes the detection of nearby stars and planets a realistic prospect \citep{pope19}.

>>>>

Exoplanet science has flourished over the last three decades. The number of known planets has doubled nearly every two years since 1995 \citep{Mamajek2016} and this accelerating rate of discovery is projected to continue for at least the next decade if current and upcoming space-based surveys deliver their expected results. However, despite extensive searches \citep[e.g.][]{2000ApJ...545.1058B,2013A&A...552A..65L,Lynch18}, neither exoplanets nor their host stars have been detected at radio frequencies, as the non-flaring emission of such systems has been too faint for current telescopes. The SKA-precursor LOFAR \citep[the LOw-Frequency ARray:][]{lofar} has unparalleled sensitivity at 150~MHz where these interactions are expected to emit significant radiation via the electron cyclotron maser instability \citep{2007P&SS...55..598Z}: with its orders-of-magnitude increase in sensitivity and survey speed, the detection of nearby stars and planets is realistic prospect \citep{pope19}.
